---
title: "P8105_hw1_yl6108"
output: html_document
---

# Session 1
```{r} 
library(ggplot2)
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains variable `r names(penguins)`.
The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean of flipper length is
`r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r} 
penguins_plot=ggplot(
  penguins, 
  aes(
   x=bill_length_mm,
   y=flipper_length_mm,
   color=species)
)+
  geom_point()

ggsave(
  "penguins_scatterplot.png",
   plot = penguins_plot
)
```
# Session 2
```{r}
library(tidyverse)

sample=rnorm(10)
   sample_df=data.frame(
     sample=sample,
     sample_0=sample>0,
     char_vec=c("A","B","C","D","E","F","G","H","I","J"),
     factor_vec=factor(
       c(1,2,3,1,2,1,2,1,2,3)
     )
)
     
mean(pull(sample_df,sample ))
mean(pull(sample_df,sample_0 ))
mean(pull(sample_df,char_vec ))
mean(pull(sample_df,factor_vec ))
```

We got the mean of random sample and logical vector, while character and factor vector didn't.

```{r, results = "hide"}
as.numeric(pull(sample_df, sample_0))
as.numeric(pull(sample_df, char_vec))
as.numeric(pull(sample_df, factor_vec))
```

When logical variables were converted  to numeric, TRUE became 1 and FALSE became 0.Character values that cannot be interpreted as numbers become NA and factor variables became 1,2 and 3.

Logical variables were identified TRUE as 1 and FALSE as 0, so we can take the mean.

